---
title: "Characterizing a built up filter"
author: "Erik Ø. Sørensen"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(scales)
```

I made an attempt at getting my fancy audio interface (MOTU M4) to work
with REW, but only ended up frustrated. Instead I grabbed my Analog
Discovery 2, which can run in network analyzer mode using the "Waveforms" 
software. Unfortunately, the the analog discovery only has a 14 bit ADC
and I haven't got an easy to use amplifier within reach, so testing
the MC output of the filter won't be possible. I also expect a substantial
amount of noise in the lower frequency, where there should be more than
60 dB of attenuation.

The setup is: BNC cable connecting output 1 from the Analog Discovery 2
generator 1 to the input of the filter, and similarly a BNC cable from the
filter output back to the oscope input 1 on the Analog Discovery.

I have used the LT-spice software to calculate the expected true
curve (under assumption of a low impedance signal generator (100 Ohm) and a
high impedance receiver at the output of the filter).

```{r include=FALSE}
lns <- readLines("ltspice_iriaa.txt", n=-1, encoding="UTF-8")
names <- strsplit(lns[1],"\t")
df_LT <- tibble(frequency = numeric(),
                vmc_db = numeric(),
                vmc_ph = numeric(),
                vmm_db = numeric(),
                vmm_ph = numeric())
for (row in lns[-1]) {
  xs <- strsplit(row, '\t')[[1]]
  f <- as.double( xs[1] )
  x1 <- str_extract_all(xs[2], "[+-]?(\\d+([.]\\d*)?(e[+-]?\\d+)?|[.]\\d+(e[+-]?\\d+)?)")[[1]]
  x2 <- str_extract_all(xs[3], "[+-]?(\\d+([.]\\d*)?(e[+-]?\\d+)?|[.]\\d+(e[+-]?\\d+)?)")[[1]]
  df_LT <- df_LT %>% add_row(frequency = f,
                             vmc_db = as.double(x1[1]),
                             vmc_ph = as.double(x1[2]),
                             vmm_db = as.double(x2[1]),
                             vmm_ph = as.double(x2[2]))
}
df_LT <- df_LT |> filter(frequency <=20000) |>
  mutate(freq_string = format(round(frequency,1), nsmall=1,trim=TRUE ))
```



```{r include=FALSE}
# Reading data from the analog discovery Waveforms software
mmr_df <- read_csv("2023-12-22T1922_R-MM.csv", comment = "#") |>
  mutate(channel = "right")
mml_df <- read_csv("2023-12-22T1924_L-MM.csv", comment = "#") |>
  mutate(channel = "left")
mm_df <- mmr_df |> bind_rows(mml_df) |>
  rename(freq = `Frequency (Hz)`,
         magnitude = `Channel 1 Magnitude (dB)`) |>
  mutate(freq_string = format(round(freq,1), nsmall=1,trim=TRUE))
df <- mm_df |> left_join(df_LT)
```

First, let's have a look at how the measurements compares to the calcuated
numbers from LT-spice:

```{r echo=FALSE}
df |> mutate(error_db = vmm_db -magnitude) |>
  ggplot(aes(x=frequency, y = error_db)) +
  geom_line() +
  theme_bw() +
  labs(x = "Frequency [Hz]", y = "Measured deviation [dB]",
       title = "Measured deviation in frequency response") +
  theme(plot.title.position = "plot") +
  scale_x_log10() +
  facet_wrap(~channel)
ggsave("../graphics/deviations.png", width = 1000, height = 600, 
       units = "px", bg = "white", scale=0.5)
```

We see that there is a lot of noise below 100Hz, which is not strange
taking the measurement equipment into account (and also some quantization error). Above 100Hz, most
of the measurements, in both channels, are about 0.25dB attenuated compared to the LT-spice numbers. This variation from the predicted numbers in the levels
isn't really a problem. 

Both channels have a slight dip around 5kHz, about 0.2dB down. This indicates
an issue with how the higher time constant is implemented. That it is the
same in both channels maybe indicates something systematic. 

As can be seen from the graph above, the channel balance is good. For 
reference, this is the deviation from perfect channel balance by frequency:

```{r echo=FALSE}
df_imbalance <- df |> pivot_wider(id_cols = frequency, names_from = channel, 
                                  values_from = magnitude) |>
  mutate(imbalance = left - right)
df_imbalance |> ggplot(aes(x=frequency, y = imbalance)) +
  geom_line() +
  theme_bw() +
  labs(x = "Frequency [Hz]", y = "Imbalance [dB]",
       title = "Measured left/right imbalance in frequency response") +
  theme(plot.title.position = "plot") +
  scale_x_log10() 

#|>
#  mutate(magnitude_difference = )
```



